---
title:  "Replication of the Epistemic Side‑Effect Effect (ESEE) in Polish on a Representative Sample"
author: "Bartosz Maćkiewicz, Marta Zaręba, Katarzyna Kuś, Katarzyna Paprzycka‑Hausman"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
#  Load packages and set global chunk defaults
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)   # data wrangling & plotting
library(ggpubr)      # convenient ggplot2 wrappers
library(ez)          # ANOVAs
library(flextable)   # nicely formatted tables
library(foreign)     # read.spss()
library(rstatix)     # pairwise tests
library(metafor)     # meta‑analysis
library(scico)       # colour palettes

#  Read the SPSS file; each row is one participant
esee <- read.spss("../data/Zbiór_UW_Marta_Zaręba_Esee_v4.sav", to.data.frame = T)

#  Keep the first non‑missing value across a set of columns
get_value <- function(x){
  if (all(is.na(x))) return(NA) 
  x[!is.na(x)]
}

get_value_empty_string <- function(x){
  if (all(str_trim(x) == "")) return(NA) 
  x[!(str_trim(x)=="")]
}

recode_likert <- function(x){
  recode(x,
         `-3 zupełnie się nie zgadzam` = -3,
         `-2` = -2,
         `-1` = -1,
         `0` = 0,
         `1` = 1,
         `2` = 2,
         `+3 w pełni się zgadzam` = 3,
         )
}

recode_binary <- function(x){
  ifelse(str_sub(x, 1, 3) == "Tak", 1, 0)
}

#  Extract key responses (the original survey used many duplicate columns)
esee <- esee %>% 
  rowwise %>% 
  mutate(
    KLikert = get_value(c_across(matches("p1_4._r1"))),
    KBinary = get_value(c_across(matches("p1_4.$"))),
    KExpl = get_value(c_across(matches("p5._w[123]$", ignore.case = FALSE))),
    KExplOther = get_value_empty_string(c_across(matches("p5._w[123]inne$", ignore.case = FALSE))),
    KProfits = get_value(c_across(matches("p1_6._r1$"))),
    Int = get_value(c_across(matches("p1_6._r2$"))),
    IntUmyślnie = get_value(c_across(matches("p1_6._r3$"))),
    IntCelowo = get_value(c_across(matches("p1_6._r4$"))),
    IntŚwiadomie = get_value(c_across(matches("p1_6._r5$"))),
    Intention = get_value(c_across(matches("p1_6._r6$"))),
    BSądził = get_value(c_across(matches("p1_6._r7$"))),
    BPrzekonany = get_value(c_across(matches("p1_6._r8$"))),
    Aware = get_value(c_across(matches("p1_6._r9$"))),
    Reasons = get_value(c_across(matches("p1_6._r10$"))),
    Condition = case_when(
      !is.na(p1_6a_r1) ~ "Help",
      !is.na(p1_6b_r1) ~ "Help",
      !is.na(p1_6c_r1) ~ "Help",
      !is.na(p1_6d_r1) ~ "Help",
      !is.na(p1_6e_r1) ~ "Help",
      !is.na(p1_6f_r1) ~ "Help",
      !is.na(p1_6g_r1) ~ "Harm",
      !is.na(p1_6h_r1) ~ "Harm",
      !is.na(p1_6i_r1) ~ "Harm",
      !is.na(p1_6j_r1) ~ "Harm",
      !is.na(p1_6k_r1) ~ "Harm",
      !is.na(p1_6l_r1) ~ "Harm",
    ),
    Scale = case_when(
      !is.na(p1_6a_r1) ~ "LIK",
      !is.na(p1_6b_r1) ~ "FC",
      !is.na(p1_6c_r1) ~ "LIK",
      !is.na(p1_6d_r1) ~ "FC",
      !is.na(p1_6e_r1) ~ "LIK",
      !is.na(p1_6f_r1) ~ "FC",
      !is.na(p1_6g_r1) ~ "LIK",
      !is.na(p1_6h_r1) ~ "FC",
      !is.na(p1_6i_r1) ~ "LIK",
      !is.na(p1_6j_r1) ~ "FC",
      !is.na(p1_6k_r1) ~ "LIK",
      !is.na(p1_6l_r1) ~ "FC",
    ),
    Form = case_when(
      !is.na(p1_6a_r1) ~ "AG",
      !is.na(p1_6b_r1) ~ "AG",
      !is.na(p1_6c_r1) ~ "PR",
      !is.na(p1_6d_r1) ~ "PR",
      !is.na(p1_6e_r1) ~ "ST",
      !is.na(p1_6f_r1) ~ "ST",
      !is.na(p1_6g_r1) ~ "AG",
      !is.na(p1_6h_r1) ~ "AG",
      !is.na(p1_6i_r1) ~ "PR",
      !is.na(p1_6j_r1) ~ "PR",
      !is.na(p1_6k_r1) ~ "ST",
      !is.na(p1_6l_r1) ~ "ST",
    )
  )

esee$KLikert <- recode_likert(esee$KLikert)
esee$KBinary <- recode_binary(esee$KBinary)

cols_to_recode <-
  c(
    "KProfits",
    "Int",
    "IntUmyślnie",
    "IntŚwiadomie",
    "IntCelowo",
    "Intention",
    "BSądził",
    "BPrzekonany",
    "Aware",
    "Reasons"
  )

for (col in cols_to_recode){
  esee[[col]] = recode_likert(esee[[col]])
}

esee$edu <- esee$e7_2

esee <- esee %>% 
  mutate(
    #  Combine Likert and binary into one three‑level factor
    KBinaryAll = case_when(
      (Scale == "FC") & (KBinary == 1) ~ "Yes",
      (Scale == "FC") & (KBinary == 0) ~ "No",
      (Scale == "LIK") & (KLikert == 0) ~ "Neither",
      (Scale == "LIK") & (KLikert > 0) ~ "Yes",
      (Scale == "LIK") & (KLikert < 0) ~ "No",
    ) 
  )

esee <- esee %>% 
  mutate(
    KExplSimple = case_when(
      str_detect(KExpl, "przekonany") ~ "B", # Belief
      str_detect(KExpl, "sprawę") ~ "Q", # Awareness
      str_detect(KExpl, "sprawy") ~ "Q", # Awareness
      str_detect(KExpl, "powody") ~ "R", # Reasons
      str_detect(KExpl, "powodów") ~ "R", # Resons
      str_detect(KExpl, "Inne") ~ "O", # Other
    )
  )

esee <- esee %>% select(ID, survey_finish_time, sex, sex2, age, year,
                        location = miasta, location2 = miasta2, location3 = miasta3, 
                        KLikert, KBinary, KBinaryAll, KExpl, KExplSimple, KExplOther, KProfits, Int, IntUmyślnie,
                        IntCelowo, IntŚwiadomie, Intention, BSądził, BPrzekonany,
                        Aware, Reasons, Condition, Scale, Form, edu)

write_csv(esee, "../data/esee_in_polish_clean.csv")
esee <- read_csv("../data/esee_in_polish_clean.csv")
```

### Simplified codebook 

- **ID** – anonymous identifier assigned by the survey platform; unique per participant.  
- **survey_finish_time** – total completion time for the whole questionnaire, recorded in **seconds** (numeric).  
- **sex** – self‑reported biological sex with four response options: *Kobieta* (female), *Mężczyzna* (male), *Inna* (other), *Nie chcę udzielać odpowiedzi* (prefer not to say).  
- **sex2** – free‑text clarification shown **only** when *sex = “Inna”*; respondents may leave it blank.  
- **age** – age bin chosen from the panel provider’s standard categories   
- **edu** – highest level of completed education (ordered from lowest to highest):  
  - *Podstawowe* — **Primary education**  
  - *Zawodowe lub policealne* — **Vocational or post‑secondary diploma**  
  - *Średnie* — **Secondary education / high‑school diploma**  
  - *Wyższe licencjackie lub inżynierskie* — **Bachelor’s or Engineering degree**  
  - *Wyższe magisterskie* — **Master’s degree (MA/MSc)**  
  - *Doktorat lub więcej* — **Doctorate or higher**
- **year** – numeric age in full years (continuous).  
- **location** – five‑level place‑of‑residence item: *wieś* (village), *małe miasto* (≤ 20 k), *średnie miasto* (20–99 k), *duże miasto* (100–500 k), *wielkie miasto* (> 500 k).  
- **location2** – additional 2‑level split of the middle categories (*20–49 k* vs. *50–99 k*).  
- **location3** – additional 2‑level split of the upper‑middle categories (*100–200 k* vs. *200–500 k*).  
- **KLikert** – agreement level to “The CEO knew that ... *harm/help* ...?” (see **Form** for details on phrasing) answered on a **7‑point Likert scale** from ‑3 (*zdecydowanie nie*, *strongly disagree*) to +3 (*zdecydowanie tak*, *strongly agree*).  
- **KBinary** – same question in a **forced‑choice** format: `1 = "Tak" ("Yes")`, `0 = "Nie" ("No")`.  
- **KBinaryAll** – unified three‑level factor combining both formats: *Yes* / *No* / *Neither* (neutral midpoint of the Likert scale).  
- **KExpl** – open‑choice justification (Polish wording) for the knowledge attribution. The form displayed depends on the respondent’s earlier answer:  
  - *Positive* claim (> 0 or `1`):
    - The CEO had reasons to believe that he would harm the environment.
    - The CEO believed that he would harm the environment. 
    - The CEO was aware that he could harm the environment.
    - Other (explain)
  - *Negative* claim (< 0 or `0`): symmetrical negations of the above.  
    - The CEO had no reasons to believe that he would harm the environment.
    - The CEO did not believe that he would harm the environment.
    - The CEO was not aware that he could harm the environment.
    - Other (explain)
  - *Neutral* (`0` only):   
    - It was not clear whether the CEO had reasons to believe that he would harm the environment.
    - It was not clear whether the CEO believed that he would harm the environment. 
    - It was not clear whether the CEO was aware that he could harm the environment.
    - Other (explain)
- **KExplSimple** – single‑letter code extracted from **KExpl**:  
  - `B` = *Belief* (CEO believed)  
  - `Q` = *Awareness* (CEO was aware)  
  - `R` = *Reasons* (CEO had reasons)  
  - `O` = *Other* / uncategorised text  
- **KExplOther** – text for `O` option  
- **KProfits** –agreement level to “The CEO knew the program would increase profits”; 7‑point Likert (‑3…+3) mirroring **KLikert**  
- **Int** –agreement level to intentionality attribution with adverb *intencjonalnie* (“intentionally”); Likert ‑3…+3.  
- **IntUmyślnie** – agreement level to intentionality attribution with adverb *umyślnie* (“deliberately”); Likert ‑3…+3.  
- **IntCelowo** – agreement level to intentionality attribution with adverb *celowo* (“purposefully”);  Likert ‑3…+3.
- **IntŚwiadomie** – agreement level to intentionality attribution with adverb *świadomie* (“knowingly”);  Likert ‑3…+3.
- **Intention** – agreement level to intention attribution with phrasing *miał intencję, aby…* (“had the intention to…”); Likert ‑3…+3.
- **BSądził** – agreement level to belief attribution using verb *sądził* (“judged / thought”); Likert ‑3…+3.   
- **BPrzekonany** – agreement level to belief attribution using phrase *był przekonany* (“believed”); Likert ‑3…+3.
- **Aware** – agreement level to awareness attribution *był świadomy* (“was aware”).  
- **Reasons** – agreement level to reason attribution *miał powody* (“had reasons”).  
- **Condition** – vignette type manipulated between subjects: `Harm` (environment worsens) or `Help` (environment improves).  
- **Scale** – response format for the knowledge item: `LIK` = 7‑point Likert, `FC` = forced choice.  
- **Form** – wording of the knowledge statement shown before the response:  
  - `AG` – **Agentive**: *Dyrektor wiedział, że zaszkodzi/pomoże środowisku* (“The CEO knew he would harm/help the environment”).  
  - `PR` – **Causal**: *Dyrektor wiedział, że wdrożenie programu pomoże/zaszkodzi środowisku* (“…that implementing the programme would help/harm the environment”).  
  - `ST` – **State‑change**: *Dyrektor wiedział, że stan środowiska się pogorszy/polepszy* (“…that the state of the environment would get worse/better”).

# Demographics

## Sex/gender

```{r}
pander::pander(table(esee$sex))
```

## Age
```{r}
esee %>% as.data.frame %>% summarise(M = mean(year), SD = sd(year)) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

## Location

```{r}
pander::pander(prop.table(table(esee$location)))
pander::pander(table(esee$location2))
pander::pander(table(esee$location3))
```

## Education

```{r}
pander::pander(table(esee$edu))
```


## Number of participants in each condition

```{r}
esee %>% 
  group_by(Condition, Scale, Form) %>% 
  summarize(n = n()) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

# Results

## Knowedge

### Likert format

```{r}
esee %>% 
  filter(Scale == "LIK") %>% 
  group_by(Form, Condition) %>% 
  summarize(
    M = mean(KLikert),
    SD = sd(KLikert),
    n = n()
  ) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

```{r}
ggbarplot(data = esee,
          x = "Condition",
          fill = "Condition",
          y = "KLikert",
          facet.by = "Form",
          add = "mean_se",
          ylim = c(-3, 3)
          ) + scico::scale_fill_scico_d()
```

### Forced-choice format 

```{r}
esee %>% 
  filter(Scale == "FC") %>% 
  group_by(Form, Condition) %>% 
  summarize(
    `%` = mean(KBinary) * 100,
    n = n()
  ) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

```{r}
ggbarplot(data = esee,
          x = "Condition",
          fill = "Condition",
          y = "KBinary",
          facet.by = "Form",
          add = "mean_se",
          ylim = c(0, 1)
          )  + scico::scale_fill_scico_d()
```

## Rest of the questions

### Splitted

```{r}
esee_long <- pivot_longer(esee, cols = all_of(cols_to_recode), names_to = "question", values_to = "response")

esee_long %>% 
  group_by(question, Scale, Form, Condition) %>% 
  summarize(
    M = mean(response),
    SD = sd(response),
    n = n()
  ) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```


```{r fig.height=15}
ggbarplot(data = esee_long,
          x = "Condition",
          fill = "Scale",
          y = "response",
          facet.by = c("question", "Form"),
          add = "mean_se",
          ylim = c(-3, 3), 
          position = position_dodge(0.9)
          ) + scico::scale_fill_scico_d()
```

### Splitted belief

```{r}
esee_long %>% 
  filter(question %in% c("BPrzekonany", "BSądził")) %>% 
  group_by(question, Form, Condition) %>% 
  summarize(
    M = mean(response),
    SD = sd(response),
    n = n()
  ) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

```{r fig}
ggbarplot(data = esee_long %>% filter(question %in% c("BPrzekonany", "BSądził")), 
          x = "Condition",
          fill = "Form",
          y = "response",
          facet.by = c("question"),
          add = "mean_se",
          ylim = c(-3, 3), 
          position = position_dodge(0.9)
          ) + scico::scale_fill_scico_d()
```


```{r}
esee_long_belief <- esee_long %>% filter(question %in% c("BPrzekonany", "BSądził"))

results <- ez::ezANOVA(data = esee_long_belief,
            dv = response,
            wid = ID,
            between = .(Condition, Form),
            within = question)

pander::pander(results$ANOVA)
```



### For all conditions combined

```{r}
esee_long <- pivot_longer(esee, cols = all_of(cols_to_recode), names_to = "question", values_to = "response")

esee_long %>% 
  group_by(question, Condition) %>% 
  summarize(
    M = mean(response),
    SD = sd(response),
    n = n()
  ) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

```{r fig.height=10}
ggbarplot(data = esee_long,
          x = "Condition",
          fill = "Condition",
          y = "response",
          facet.by = c("question"),
          add = "mean_se",
          ylim = c(-3, 3), 
          position = position_dodge(0.9)
          ) + scico::scale_fill_scico_d()
```


# Further statistical analyses

## Is the formulation of the question statistically significant?

### ANOVA for responses on Likert scale

```{r}
esee$participant <- 1:nrow(esee)
results <- ez::ezANOVA(data = esee %>% filter(Scale == "LIK"),
            dv = KLikert,
            wid = participant,
            between = .(Condition, Form))

pander::pander(results$ANOVA)
```

### Pairwise comparisons for responses on Likert scale

```{r}
esee %>% 
  filter(Scale == "LIK") %>% 
  group_by(Condition) %>% 
  pairwise_t_test(KLikert ~ Form) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

### Pairwise comparisons for responses in fored-choice format

```{r}
binary_tally <- esee %>% 
  filter(Scale == "FC") %>% 
  group_by(Condition, Form, KBinary) %>% 
  tally()

binary_tally <- binary_tally %>% 
  group_by(Condition) %>% 
  pivot_wider(names_from = c("KBinary"), values_from = "n")

binary_tally_harm <- binary_tally %>%
  filter(Condition == "Harm") %>% 
  column_to_rownames("Form") %>% 
  select(everything(), -Condition) %>% 
  pairwise_fisher_test(., p.adjust.method = "none") %>% 
  mutate(Condition = "Harm", .before = group1)

binary_tally_help <- binary_tally %>% 
  filter(Condition == "Help") %>% 
  column_to_rownames("Form") %>% 
  select(everything(), -Condition) %>% 
  pairwise_fisher_test(., p.adjust.method = "none") %>% 
  mutate(Condition = "Help", .before = group1)

rbind(binary_tally_harm, binary_tally_help) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

## Justifications

# Table with three formulations separately

```{r}
explanations <- esee %>% 
  group_by(Scale, Form, Condition, KBinaryAll, KExplSimple) %>% 
  summarize(n = n()) %>% 
  group_by(Scale, Form, Condition, KBinaryAll) %>% 
  mutate(`Percent` = n/sum(n) * 100) 

explanations %>% 
  pivot_wider(names_from = c("KExplSimple"), values_from = c("Percent", "n")) %>% 
  select(Scale, Form, Condition, Kc = KBinaryAll, `Percent_B`, n_B, `Percent_Q`, n_Q, `Percent_R`, n_R, `Percent_O`, n_O) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

### Justifications for binary choice

```{r}
ggbarplot(y = "Percent",
          fill = "KExplSimple",
          x = "KBinaryAll",
          facet.by = c("Form", "Condition"),
          data = explanations %>% filter(Scale == "FC"),
          position = position_dodge(0.9)
          )
```


### Justifications for Likert scale 

```{r}
ggbarplot(y = "Percent",
          fill = "KExplSimple",
          x = "KBinaryAll",
          facet.by = c("Form", "Condition"),
          data = explanations %>% filter(Scale == "LIK"),
          position = position_dodge(0.9)
          )
```

### Table with three formulations together

```{r}
explanations <- esee %>% 
  group_by(Scale, Condition, KBinaryAll, KExplSimple) %>% 
  summarize(n = n()) %>% 
  group_by(Scale, Condition, KBinaryAll) %>% 
  mutate(`Percent` = n/sum(n) * 100) 

explanations %>% 
  pivot_wider(names_from = c("KExplSimple"), values_from = c("Percent", "n")) %>% 
  select(Scale, Condition, Kc = KBinaryAll, `Percent_B`, n_B, `Percent_Q`, n_Q, `Percent_R`, n_R, `Percent_O`, n_O) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

### Justifications 

```{r}
ggbarplot(y = "Percent",
          fill = "KExplSimple",
          x = "KBinaryAll",
          facet.by = c("Scale", "Condition"),
          data = explanations,
          position = position_dodge(0.9)
          )
```

## Meta-analysis

```{r} 
lik_meta <- esee %>% 
  filter(Scale == "LIK") %>% 
  group_by(Condition, Form) %>% 
  summarize(M = mean(KLikert),
            SD = sd(KLikert),
            n = n()
            ) %>% 
  pivot_wider(names_from = "Condition", values_from = c("M", "SD", "n")) %>% 
  mutate(Scale = "LIK", .before = Form) %>% 
  mutate(d = compute.es::mes(M_Harm, M_Help, SD_Harm, SD_Help, n_Harm, n_Help, verbose = F)$d,
         var = compute.es::mes(M_Harm, M_Help, SD_Harm, SD_Help, n_Harm, n_Help, verbose = F)$var.d,
         )



ww_meta <- esee %>% 
  filter(Scale == "FC") %>% 
  group_by(Condition, Form, KBinary) %>% 
  tally() %>% 
  group_by(Condition, Form, KBinary) %>% 
  pivot_wider(names_from = c("Condition", "KBinary"), values_from = c("n")) %>% 
  mutate(Scale = "FC") %>% 
  mutate(
    or = (Harm_1 * Help_0) / (Help_0 * Harm_0),
    vor = (1/Harm_1) + (1/Harm_0) +(1/Help_1) +(1/Help_0),
    d = log(or) * (sqrt(3)/pi),
    var = vor * (3/(pi**2))
  )
  
meta <- bind_rows(lik_meta, ww_meta) %>% 
  mutate(StudySlab = str_c(Scale, " ", Form), .before = Scale)
```

```{r}
fit <- rma.uni(yi = d,
               vi = var,
               slab = StudySlab,
               data = meta,
               test = "t",
               method = "REML",
              )

```

```{r}
summary(fit)
```

### Forest plot

```{r forest-plot-all}
forest(fit, ilab = meta$Scale, ilab.xpos = -0.5, ilab.pos = 2)
```

### Meta-regression

```{r}
fit <- rma.mv(yi = d,
               V = var,
               slab = StudySlab,
               data = meta,
               test = "t",
               method = "REML",
               mods = ~ Scale + Form 
              )
summary(fit)
```

# Appendix: responses to Likert scane questions collapsed into three categories

## Results

### Knowedge

#### Categorized Likert format and Forced-choice format

```{r}
esee %>% 
  group_by(Form, Condition, Scale, KBinaryAll) %>% 
  summarize(
    n = n(),
  ) %>% 
  group_by(Form, Condition, Scale) %>% 
  mutate(Percent = n * 100 / sum(n)) %>% 
  pivot_wider(names_from = "KBinaryAll", values_from = c("n", "Percent")) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

```{r}
plots_df <- esee %>% 
  group_by(Form, Condition, Scale, KBinaryAll) %>% 
  summarize(
    n = n(),
  ) %>% 
  group_by(Form, Condition, Scale) %>% 
  mutate(Percent = n * 100 / sum(n)) 
  
ggbarplot(data = plots_df,
          x = "Scale",
          fill = "KBinaryAll",
          y = "Percent",
          facet.by = c("Condition", "Form"),
          position = position_dodge(0.9)
          ) + scico::scale_fill_scico_d()
```

## Rest of the questions

### For all conditions combined

```{r}
esee_long <- pivot_longer(esee, cols = all_of(cols_to_recode), names_to = "question", values_to = "response")
esee_long <- esee_long %>% mutate(response_bin = case_when(
        (response == 0) ~ "Neither",
        (response > 0) ~ "Yes",
        (response < 0) ~ "No"
  
))

esee_long %>% 
  group_by(question, Condition, response_bin) %>% 
  summarize(n = n()) %>% 
  group_by(question, Condition) %>% 
  mutate( Percent = n * 100 /sum(n)) %>% 
  pivot_wider(names_from = "response_bin", values_from = c("n", "Percent")) %>% 
  flextable() %>%
  colformat_double(digits = 2) %>%
  fit_to_width(11.5)
```

```{r fig.height=10}
esee_long_plot <- esee_long %>% 
  group_by(question, Condition, response_bin) %>% 
  summarize(n = n()) %>% 
  group_by(question, Condition) %>% 
  mutate( Percent = n * 100 /sum(n))
  
ggbarplot(data = esee_long_plot,
          x = "Condition",
          fill = "response_bin",
          y = "Percent",
          facet.by = c("question"),
          add = "mean_se",
          position = position_dodge(0.9)
          ) + scico::scale_fill_scico_d()
```